---
title: "Simulation"
author: "Yaduo Wang"
date: "2023-11-12"
output: github_document
---

```{r}
library(tidyverse)

set.seed(1)
```

## Let's similate something

I have a function take sample of size n from the population with mu and sigma.
```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data |> 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
sim_mean_sd(30)
```

## Let's simulate a lot
Let's start with a for loop.
Repeat 100 times of the function and generate a dataframe with 100 sample means and sample sd with sample 30 under the normal distribution with mean = 2 and sigma = 3. 
```{r}
#define an output.
output = vector("list", length = 100)

#
for (i in 1:100) {
  output[[i]] = sim_mean_sd(30)
  
}
bind_rows(output)
```

Let's use a loop function.
generate the same results. Rerun the function for 100 times and get 100 sample means and standard deviations. 
```{r}
sim_results = 
  rerun(100, sim_mean_sd(30)) |> 
  bind_rows()

```

Find the average and standard deviations for the 100 sample mean.
```{r}
sim_results |> 
    ggplot(aes(x = mu_hat)) + 
  geom_density()

sim_results |> 
    ggplot(aes(x = sigma_hat)) + 
  geom_density()

sim_results |> 
  summarize(
    average_sample_mean = mean(mu_hat),
    sd_samp_mean = sd(mu_hat)
  )
```

## Let's try other sample sizes. 
```{r}
n_list = list(
  "n = 30" = 30,
  "n = 60" = 60,
  "n = 120" = 120,
  "n = 240" = 240
)

output = vector("list", 4)

# run every sample size for 100 times

for (i in 1:4){
  output[[i]] = rerun(100, sim_mean_sd(n = n_list[[i]])) |> 
    bind_rows()
}

## CONFUSE!!!
sim_result = 
  tibble(
  n = c(30, 60, 120, 240)
) |> 
  mutate(
    output_lists = map(.x = n, ~ rerun(100, sim_mean_sd(.x))),
    estimate_df = map(output_lists, bind_rows)
  ) |> 
  select(-output_lists) |> 
  unnest(estimate_df)
```

```{r}
sim_result |> 
  mutate(
    sample_size = str_c("n = ", n),
    sample_size = fct_inorder(sample_size)) |> 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin()
```

```{r}
sim_result |> 
  group_by(n) |> 
  summarize(
    avg_sample_mean = mean(mu_hat),
    sd_samp_mean = sd(mu_hat)
  )
```

